CA Affordabulity

### 2020-09-16 Untitled.Rmd
Update Untitled.Rmd

ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18)
rm(ear13,ear14,ear15,ear16,ear17,ear18)
save(ear,file="Data/EAR/ear.rds")

hcf <- filter(ear,QuestionName=='WR 6 HCF DW Charges')
x <- filter(ear, QuestionName=='')
```

@@

```{r rates, echo=FALSE, include=TRUE, message=FALSE,warning=FALSE, results='asis'}
rates$Private <- 0
rates$Private[which(rates$Ownership=="Private")]<-1
ggplot(rates, aes(x=as.factor(hh_sizes), y=total_bill_by_hhsize, colour=Ownership)) +
  geom_boxplot()

@@

@@

@@

## Shut-offs

>>>>

ear <- bind_rows(ear13,ear14,ear15,ear16,ear17,ear18)
rm(ear13,ear14,ear15,ear16,ear17,ear18)
save(ear,file="Data/EAR/ear.rds")
ear$QCat<-substr(ear$QuestionName,1,2)

wr <- filter(ear,QCat=="WR")

hcf <- ear %>% 
  filter(Year==2017 & (QuestionName=='WR 6 HCF DW Charges' |QuestionName=='WR 12 HCF DW Charges' )) %>% 
  distinct(.keep_all=TRUE) %>%
  mutate(ConsLevel=QuestionName,
         MonthlyBill=as.numeric(QuestionResults)) %>%
  select(PWSID,ConsLevel,MonthlyBill)

#hcf12 <- filter(ear, QuestionName =="WR 12 HCF DW Charges")

@@

```{r rates, echo=FALSE, include=TRUE, message=FALSE,warning=FALSE, results='asis'}
r <- left_join(b,hcf,by="PWSID")
wr_types <- wr %>% 
  filter(QuestionName=="WR Type") %>% 
  group_by(PWSID) %>% 
  mutate(maxYear=max(Year)) %>% 
  ungroup() %>% 
  filter(Year==maxYear)

no_rates <- wr_types %>% 
  filter(QuestionResults=="-" | QuestionResults=="N/A") %>% 
  mutate(rateType=QuestionResults) %>%
  distinct(PWSID,.keep_all=TRUE)

has_rates <- filter(wr, QuestionName=="WR Type") %>% distinct(PWSID)

r <- anti_join(r,no_rates,by="PWSID")
r <- semi_join(r,has_rates,by="PWSID")

r$Private <- 0
r$Private[which(r$Ownership=="Private")]<-1
r$MonthlyBill[which(r$MonthlyBill>1000)]<-NA
ggplot(filter(r, MonthlyBill>0), aes(x=as.factor(ConsLevel), y=MonthlyBill, colour=Ownership)) +
  geom_boxplot()

mr1<-lm(MonthlyBill~Private,data=r[which(r$ConsLevel=="WR 6 HCF DW Charges" & r$MonthlyBill>0),])
mr2<-lm(MonthlyBill~Private,data=r[which(r$ConsLevel=="WR 12 HCF DW Charges"& r$MonthlyBill>0),])

mr1.w<-lm(MonthlyBill~Private,data=r[which(r$ConsLevel=="WR 6 HCF DW Charges" & r$MonthlyBill>0),],weights=r$D_POPULATI[which(r$ConsLevel=="WR 6 HCF DW Charges" & r$MonthlyBill>0)])
mr2.w<-lm(MonthlyBill~Private,data=r[which(r$ConsLevel=="WR 12 HCF DW Charges"& r$MonthlyBill>0),],weights=r$D_POPULATI[which(r$ConsLevel=="WR 12 HCF DW Charges"& r$MonthlyBill>0)])

rates$Private <- 0
rates$Private[which(rates$Ownership=="Private")]<-1
ggplot(rates, aes(x=as.factor(hh_sizes), y=total_bill_by_hhsize, colour=Ownership)) +
  geom_boxplot()

@@

ggplot(filter(rates,hh_sizes==3), aes(x=log(D_POPULATI+1), y=log(total_bill_by_hhsize), color=as.factor(Private), shape=as.factor(Private))) +
  geom_point()

ggplot(filter(r,MonthlyBill>0 & ConsLevel=="WR 6 HCF DW Charges" & D_POPULATI>10000), aes(x=log(D_POPULATI), y=log(MonthlyBill), color=as.factor(Private))) +
  geom_point() + 
  geom_smooth(method=lm)

@@

r1<-lm(log(MonthlyBill)~log(D_POPULATI+1)+Private,data=r[which(r$ConsLevel=="WR 6 HCF DW Charges" & r$MonthlyBill>0 & r$D_POPULATI>3300),])
r2<-lm(log(MonthlyBill)~log(D_POPULATI+1)+Private,data=r[which(r$ConsLevel=="WR 12 HCF DW Charges" & r$MonthlyBill>0 & r$D_POPULATI>3300),])

stargazer(r1,r2,type='html')

@@

## Shut-offs
```{r shutoffs}
conn <- ear %>% filter(SectionName=="Connections" & Year==2018)
conn_sfr <- conn %>% filter(QuestionName=="SFR Potable Total" & Year==2018)
conn_mfr <- conn %>% filter(QuestionName=="MFR Potable Total" & Year==2018)
conn_total <- conn %>% filter(QuestionName=="T Potable Total" & Year==2018)

shutoffs <- ear %>% filter(QuestionName=="")
```
